Think again?\\ Optimal mental simulation tracks problem difficulty

### 2015-01-30 manuscript.tex
Add node about arrow in experiment figure
Update results; add statistics about bounces

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. \emph{Left:} the initial screen presented to the participant. \emph{Middle:}  the screen is occluded after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. \emph{Right:} the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure*}

@@

For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 1000 bootstrap samples. Participants had an average response time of \AvgRT{} milliseconds (\StdRT{}ms), excluding catch trials. There were significant effects of both feedback type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between feedback type and hole size (\RTFull{}). However, there was only evidence for a difference in reaction times by hole size in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole. Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.

@@

In addition, we found that response time is affected by the number of bounces during feedback; participants were slower to respond as more bounces were added. While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost. \TODO{Can we add statistics here? E.g., how much additional time, and something showing that this is above and beyond difficulty (intercept differences with quadratic fits)?} This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation. We will use this theory to further explain expected reaction times in \TODO{Add section here}.

>>>>

\begin{figure*}[t]
    \begin{center}
        \includegraphics[width=\textwidth]{figures/experiment.png}
        \caption{\textbf{Example experimental trial.} Each panel shows a different part of the trial. \emph{Left:} the initial screen presented to the participant. The arrow was not part of the actual stimuli; it has been added to reflect the animation that participants observed after pressing ``space''. \emph{Middle:}  the screen is occluded after observing the stimulus presentation. The faded gray line shows the path the ball took during the initial presentation. \emph{Right:} the final position of the ball, after observing the feedback. As in the middle panel, the faded gray line shows the path of the ball.}
        \label{fig:experiment}
    \end{center}
\end{figure*}

@@

For all analyses of response time, we computed averages using bootstrapped logarithmic means (exponential of the mean of the log response times), using 1000 bootstrap samples. Participants had an average response time of \AvgRT{}, excluding catch trials. There were significant effects of both feedback type (\RTHoleClass{}) and hole size (\RTHoleSize{}) on response time, as well as an interaction between feedback type and hole size (\RTFull{}). However, there was only evidence for a difference in reaction times by hole size in the case of the ``far in'' (FI) trials ($p<0.001$), in which the ball went straight through the center of the hole. Figure \ref{fig:pct-vs-rt} (middle subplot) shows the response times as a function of feedback type and hole size.

@@

In addition, we found that response time is affected by the number of bounces during feedback. Participants were fastest to respond on trials with zero bounces (\RTZeroBounces{}), slower to respond on trials with once bounce (\RTOneBounces{}), and slowest to respond on trials with two bounces (\RTTwoBounces{}). While this may be partially modulated by difficulty---people make more variable predictions as bounces are added \cite{Smith:2013fc}, and more variable trials have longer reaction times---there appears to be an additional time cost. For each number of bounces, we fit participants' response times to a second-order polynomial function of their responses. From these fits, we see that the intercepts are significantly different across the different numbers of bounces: for zero bounces, the intercept was \InterceptZeroBounces{}; for one bounce, it was \InterceptOneBounces{}; and for two bounces, it was \InterceptTwoBounces{}. This suggests that it takes additional time to resolve a collision between the ball and a wall in the course of a simulation. We will use this theory to further explain expected reaction times in \TODO{Add section here}.
